Effectiveness of community-based marine reserves in small-scale fisheries

### 2018-09-02 docs/paper/Villasenor-Derbez.Rmd
Added Arturo to ms

---
title: "Effectiveness of community-based marine reserves in small-scale fisheries"
rtitle: "Community-based marine reserves: `r Sys.Date()`"
author: "Juan Carlos Villaseñor-Derbez$^{1,*}$, Eréndira Aceves-Bueno$^{1}$, Álvin Suarez$^{2}$, Stuart Fulton$^{2}$, Jorge Torre$^{2}$"
institution: "$^{1}$Bren School of Environmental Science and Management, University of California, Santa Barbara, Santa Barbara, CA, USA\\newline
$^{2}$Comunidad y Biodiversidad A.C.,  Guaymas, Mexico"
corrauth: "Juan Carlos Villaseñor-Derbez, Bren Hall, University of California, Santa Barbara, Santa Barbara, CA, 93106"
email: "jvillasenor@bren.ucsb.edu"
abstract: "Coastal marine ecosystems provide livelihoods for small-scale fishers and coastal communities around the world. Artisanal fisheries face great challenges since they are difficult to monitor, enforce, and manage. Combining territorial user rights for fisheries (TURF) with no-take marine reserves to create TURF-reserves is believed to improve the performance of small-scale fisheries by buffering fisheries from environmental variability and management errors, while ensuring that fishers reap the benefits of conservation investments. In the last 4 years, 45 TURF reserves have been implemented in Mexico, but their effectiveness has not been formally evaluated. We combine causal inference techniques and a social-ecological systems framework to provide a holistic evaluation of community-based TURF reserves in three coastal communities in Mexico. We find that while reserves have not yet achieved their stated goal of increasing lobster densities, they continue to receive significant support from the fishing communities. A lack of ecological and socioeconomic effects or reserves likely results from a combination of factors. First, the lobster fisheries are already well managed, and it is unlikely that reserves might have a detectable effect. Second, reserves are not large enough to protect lobster’s home ranges. Third, some of these reserves might be too young for the effects to show. However, these reserves have shaped small-scale fishers’ way of thinking about marine management, which can provide a foundation for establishing additional, larger marine reserves needed to effectively conserve mobile species."
keywords: "Marine Protected Areas, Marine Conservation, Small-Scale Fisheries, Citizen Science, TURF-reserves, Social-Ecological Systems"
output:
  bookdown::pdf_document2:
    keep_tex: yes
    template: template.tex
header-includes:
  - \usepackage{float}
  - \floatplacement{figure}{H}
---

>>>>

---
title: "Effectiveness of community-based marine reserves in small-scale fisheries"
rtitle: "Community-based marine reserves: `r Sys.Date()`"
author: "Juan Carlos Villaseñor-Derbez$^{1,*}$, Eréndira Aceves-Bueno$^{1}$, Álvin Suarez$^{2}$, Arturo Hernández-Velasco$^{2}$, Stuart Fulton$^{2}$, Jorge Torre$^{2}$"
institution: "$^{1}$Bren School of Environmental Science and Management, University of California, Santa Barbara, Santa Barbara, CA, USA\\newline
$^{2}$Comunidad y Biodiversidad A.C.,  Guaymas, Mexico"
corrauth: "Juan Carlos Villaseñor-Derbez, Bren Hall, University of California, Santa Barbara, Santa Barbara, CA, 93106"
email: "jvillasenor@bren.ucsb.edu"
abstract: "Coastal marine ecosystems provide livelihoods for small-scale fishers and coastal communities around the world. Artisanal fisheries face great challenges since they are difficult to monitor, enforce, and manage. Combining territorial user rights for fisheries (TURF) with no-take marine reserves to create TURF-reserves is believed to improve the performance of small-scale fisheries by buffering fisheries from environmental variability and management errors, while ensuring that fishers reap the benefits of conservation investments. In the last 4 years, 45 TURF reserves have been implemented in Mexico, but their effectiveness has not been formally evaluated. We combine causal inference techniques and a social-ecological systems framework to provide a holistic evaluation of community-based TURF reserves in three coastal communities in Mexico. We find that while reserves have not yet achieved their stated goal of increasing lobster densities, they continue to receive significant support from the fishing communities. A lack of ecological and socioeconomic effects or reserves likely results from a combination of factors. First, the lobster fisheries are already well managed, and it is unlikely that reserves might have a detectable effect. Second, reserves are not large enough to protect lobster’s home ranges. Third, some of these reserves might be too young for the effects to show. However, these reserves have shaped small-scale fishers’ way of thinking about marine management, which can provide a foundation for establishing additional, larger marine reserves needed to effectively conserve mobile species."
keywords: "Marine Protected Areas, Marine Conservation, Small-Scale Fisheries, Citizen Science, TURF-reserves, Social-Ecological Systems"
output:
  bookdown::pdf_document2:
    keep_tex: yes
    template: template.tex
header-includes:
  - \usepackage{float}
  - \floatplacement{figure}{H}
---

### 2018-09-02 docs/paper/Villasenor-Derbez.tex
Added Arturo to ms

\def\keyFont{\fontsize{8}{11}\helveticabold }
\def\firstAuthorLast{Villaseñor-Derbez {et~al.}}
\def\Authors{Juan Carlos Villaseñor-Derbez\(^{1,*}\), Eréndira Aceves-Bueno\(^{1}\),
Álvin Suarez\(^{2}\), Stuart Fulton\(^{2}\), Jorge Torre\(^{2}\)}
% Affiliations should be keyed to the author's name with superscript numbers and be listed as follows: Laboratory, Institute, Department, Organization, City, State abbreviation (USA, Canada, Australia), and Country (without detailed address information such as city zip codes or street names).
% If one of the authors has a change of address, list the new address below the correspondence details using a superscript symbol and use the same symbol to indicate the author in the author list.
\def\Address{\(^{1}\)Bren School of Environmental Science and Management, University
of California, Santa Barbara, Santa Barbara, CA,
USA\newline \(^{2}\)Comunidad y Biodiversidad A.C., Guaymas, Mexico}
% The Corresponding Author should be marked with an asterisk
% Provide the exact contact address (this time including street name and city zip code) and email of the corresponding author
\def\corrAuthor{Juan Carlos Villaseñor-Derbez, Bren Hall, University of California,
Santa Barbara, Santa Barbara, CA, 93106}

@@

\title[Community-based marine reserves: 2018-08-16]{Effectiveness of community-based marine reserves in small-scale
fisheries}

>>>>

\def\keyFont{\fontsize{8}{11}\helveticabold }
\def\firstAuthorLast{Villaseñor-Derbez {et~al.}}
\def\Authors{Juan Carlos Villaseñor-Derbez\(^{1,*}\), Eréndira Aceves-Bueno\(^{1}\),
Álvin Suarez\(^{2}\), Arturo Hernández-Velasco\(^{2}\), Stuart
Fulton\(^{2}\), Jorge Torre\(^{2}\)}
% Affiliations should be keyed to the author's name with superscript numbers and be listed as follows: Laboratory, Institute, Department, Organization, City, State abbreviation (USA, Canada, Australia), and Country (without detailed address information such as city zip codes or street names).
% If one of the authors has a change of address, list the new address below the correspondence details using a superscript symbol and use the same symbol to indicate the author in the author list.
\def\Address{\(^{1}\)Bren School of Environmental Science and Management, University
of California, Santa Barbara, Santa Barbara, CA,
USA\newline \(^{2}\)Comunidad y Biodiversidad A.C., Guaymas, Mexico}
% The Corresponding Author should be marked with an asterisk
% Provide the exact contact address (this time including street name and city zip code) and email of the corresponding author
\def\corrAuthor{Juan Carlos Villaseñor-Derbez, Bren Hall, University of California,
Santa Barbara, Santa Barbara, CA, 93106}

@@

\title[Community-based marine reserves: 2018-08-30]{Effectiveness of community-based marine reserves in small-scale
fisheries}
